RNApyro

### 2012-10-04 Recomb/methods_RECOMB.tex
advanced method

\subsection{Energy Model}
The energy we will be composed of two function, $\text{ES}^{\beta}_{ab\to a'b'}$ and 
$\text{EI}^{\Omega}_{(i,j),ab}$. The former is equal to the 
stacking energy of the base pair with nucleotides $ab$ on top of the base pair with nucleotides 
$a'b'$, as set in the NNDB~\cite{Turner2010}. If one of the base pair is not valid (i.e. not in 
$\{\text{GU},\text{UG},\text{CG},\text{GC}, \text{AU or UA}\}$, the value is a parameter 
$\beta \in [1,\infty]$. This allows
to completely forbid a sequence where a base pair is non valid, when $\beta = \infty$ or only 
penalize it.
$\text{EI}^{\Omega}_{(i,j), a'b'}$ is the average of the sum of differences between the isostericity
of base pairs at positions $(i,j)$ in $\Omega$ and $s_is_j$, and the isostericity of base pairs
 at positions $(i,j)$ in $\Omega$ and $ab$. If gives us an indication 
 if the base pair $ab$ is more isosteric to the set $\Omega$ than the one on the sequence 
 $\omega$. Formally, given $s$, $\Omega$, two positions $(i,S_i)$ and two nucleotides $a,b\in B$:
 $$
 	\text{EI}^{\Omega}_{(i,j),ab}:=
	\frac{
		\displaystyle
		\sum_{s'\in\Omega}
		\left(
			\text{ISO}((s_i',s_j'),(a,b))
		\right)-
		\left(
			\text{ISO}((s_i',s_j'),(s_i,s_j))		
		\right)
	}{
		\displaystyle
		|\Omega|
	}
 $$
  Where $\text{ISO}((a',b'),(a,b))$ is the isostericity values 
 between a the canonical base pairs $(a',b')$ and $(a,b)$  as defined in~\cite{Stombaugh2009}. 
 Let be $\alpha\in[0,1]$, it 
 will be used to balance the weight given to the stacking energy or the isostericity.

>>>>

\subsection{Energy Model}
The energy we will be composed of two function, $\text{ES}^{\beta}_{ab\to a'b'}$ and 
$\text{EI}^{\Omega}_{(i,j),ab}$. The former is equal to the 
stacking energy of the base pair with nucleotides $ab$ on top of the base pair with nucleotides 
$a'b'$, as set in the NNDB~\cite{Turner2010}. If one of the base pair is not valid (i.e. not in 
$\{\text{GU},\text{UG},\text{CG},\text{GC}, \text{AU or UA}\}$, the value is a parameter 
$\beta \in [1,\infty]$. This allows
to completely forbid a sequence where a base pair is non valid, when $\beta = \infty$ or only 
penalize it.
$\text{EI}^{\Omega}_{(i,j), a'b'}$ is the average of the sum of differences between the isostericity
of base pairs at positions $(i,j)$ in $\Omega$ and $s_is_j$, and the isostericity of base pairs
 at positions $(i,j)$ in $\Omega$ and $ab$. If gives us an indication 
 if the base pair $ab$ is more isosteric to the set $\Omega$ than the one on the sequence 
 $\omega$. Formally, given $s$, $\Omega$, two positions $(i,S_i)$ and two nucleotides $a,b\in B$:
 $$
 	\text{EI}^{\Omega}_{(i,j),ab}:=
	\frac{
		\displaystyle
		\sum_{s'\in\Omega}
		\left(
			\text{ISO}((s_i',s_j'),(a,b))
		\right)-
		\left(
			\text{ISO}((s_i',s_j'),(s_i,s_j))		
		\right)
	}{
		\displaystyle
		|\Omega|
	}
 $$
  Where $\text{ISO}((a',b'),(a,b))$ is the isostericity value 
 between  the canonical base pairs $(a',b')$ and $(a,b)$  as defined in~\cite{Stombaugh2009}. 
 Let be $\alpha\in[0,1]$, it 
 will be used to balance the weight given to the stacking energy and the isostericity.
